Ecuador plant species BIEN data

### 2023-01-12 code/L0/L0_Ecuador_plants_BIEN.Rmd
Add bdvis package for summary

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(mde)
library(DataExplorer)
library(summarytools)
```

@@

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
#plot_missing(Ecuador_BIEN_occ)
#plot_bar(Ecuador_BIEN_occ)
```

@@

```{r}
Ecuador_BIEN_traits_summary <- dfSummary(Ecuador_BIEN_traits, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_BIEN_traits_summary, method = "render")
view(Ecuador_BIEN_traits_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```

>>>>

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(mde)
library(DataExplorer)
library(summarytools)
library(bdvis)
```

@@

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
```

@@

```{r}
Ecuador_BIEN_traits_summary <- dfSummary(Ecuador_BIEN_traits, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_BIEN_traits_summary, method = "render")
view(Ecuador_BIEN_traits_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```
```{r}
#using bdvis package
Ecuador_BIEN_occ <- format_bdvis(Ecuador_BIEN_occ, Latitude = "latitude", Longitude = "longitude", Date_collected = "date_collected", Scientific_name = "verbatim_scientific_name")
bdsummary(Ecuador_BIEN_occ)
```
```{r}
bdcalendarheat(Ecuador_BIEN_occ)
bdcomplete(Ecuador_BIEN_occ)
distrigraph(Ecuador_BIEN_occ, ptype = "species")
distrigraph(Ecuador_BIEN_occ, ptype = "efforts")
distrigraph(Ecuador_BIEN_occ, ptype = "cell")
distrigraph(Ecuador_BIEN_occ, ptype = "effortspecies")
mapgrid(Ecuador_BIEN_occ, ptype = "species", region = "Ecuador")
```
